### 2016-06-06 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Edits to hose stream plotting script; can now print values for tables in report
Plotting/sorting script prints out values for tables in hose stream report; fixed typo in All_Times

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lcccccccc}
\toprule
 &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
\\
 &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   & -0.3 $\pm0.1$   & & 0.9 $\pm0.2$    & 0.9 $\pm0.2$    & & 0.7 $\pm0.1$    & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.1 $\pm0.4$) & (3.2 $\pm0.6$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.4 $\pm0.4$  & &   1.3 $\pm0.2$  & 1.4 $\pm0.2$    & &   0.9 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.8 $\pm0.5$) & (3.1 $\pm0.6$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
\\ \midrule
 &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
\\
 &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{2}{*}{\textit{Straight}} &
\small{m/s}   &   1.7 $\pm0.3$   & \multicolumn{2}{c}{1.9 $\pm0.3$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Smooth Bore}} &
\small{m/s}   &   1.7 $\pm0.3$  &  \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
\\
% \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% \begin{tabular}{@{}c@{}} -0.3 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} 
% \\ \multicolumn{9}{c}{} \\
% \textit{Narrow Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% 1.1 $\pm0.2$ & & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & & 0.8 $\pm0.1$ & 0.7 $\pm0.1$
% \\ \multicolumn{9}{c}{} \\
% \textit{Wide Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% 2.4 $\pm0.4$ & & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
% \\ \midrule
%  &  & \multicolumn{3}{c}{\large --- 180 gpm ---} & \multicolumn{4}{c}{} 
% \\
%  &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
% \\
% \textbf{Stream} & \textbf{Units} &
% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &  &
% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
% \multicolumn{4}{c}{} 
% \\
% \midrule
% \textit{Straight} &  \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
% 1.7 $\pm0.3$ &  & 1.9 $\pm0.3$ & \multicolumn{4}{c}{} 
% \\ \multicolumn{9}{c}{} \\
% \textit{Smooth Bore} & 
% 1.7 $\pm0.3$ &  & 2.0 $\pm0.4$ & \multicolumn{4}{c}{}
% \\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average gas velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
\begin{tabular}{lccccccc}
\toprule
 & \multicolumn{3}{c}{\underline{Room A}} &  & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} &  & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ &  &
-0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
\\ \multicolumn{8}{c}{} \\
\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ &  & 
0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
\\ \multicolumn{8}{c}{} \\
\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ &  & 
2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.2 $\pm0.04$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 0.4 $\pm0.1$ & 1.0 $\pm0.2$ & 0.8 $\pm0.1$ & 1.0 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
\\ \midrule
 & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.6 $\pm0.1$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier

>>>>

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lcccccccc}
\toprule
 &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
\\
 &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   & -0.3 $\pm0.1$   & &  0.9 $\pm0.2$  &  0.9 $\pm0.2$  & &  0.7 $\pm0.1$  & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.8 $\pm0.1$ \\ &
\small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  2.5 $\pm0.4$  & &   1.3 $\pm0.2$   &  1.4 $\pm0.2$   & &   1.2 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
\small{(mph)} & (5.6 $\pm1.0$) & &  (2.8 $\pm0.5$)  & (3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) & (1.7 $\pm0.3$) 
\\ \midrule
 &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
\\
 &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{2}{*}{\textit{Straight}} &
\small{m/s}   &   1.8 $\pm0.3$   & \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Smooth Bore}} &
\small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} 
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
\begin{tabular}{lcccc}
\toprule
 &  & \multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
\\ \midrule
 & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$)  
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
\begin{tabular}{lccccc}
\toprule
 & & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.4 $\pm0.1$   &   1.1 $\pm0.2$  &   0.9 $\pm0.2$   &  1.1 $\pm0.2$  \\ & 
\small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$)
\\ \midrule
 & & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier
